On Star Formation at Dynamical Resonances of the Bar

### 2019-12-26 paper/ms.tex
Update softening lengths
Update ms.tex
Update abstract

@@

% Abstract of the paper
\begin{abstract}
Stars are known to be captured at the dynamical resonances of the Milky Way
bar, forming moving groups that are seen in the solar neighborhood. In
principle, gas can also be captured at these resonances which, if allowed to
cool, might trigger star formation -- predicting an enhanced number of
star-forming regions at these resonances. However, the efficiency of stellar
and radiation feedback may suppress the star formation process.
\end{abstract}

@@

\section{Introduction}

This is a simple template for authors to write new MNRAS papers.
See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
for a full user guide.

All papers should start with an Introduction section, which sets the work
in context, cites relevant earlier studies in the field by \citet{Others2013},
and describes the problem the authors aim to solve \citep[e.g.][]{Author2012}.

\section{Methods, Observations, Simulations etc.}

@@

\begin{table}
\begin{tabular}{cccc}
resolution level & $m_{\text{DM}}$      & $m_{\text{b}}$    & $\epsilon$        \\
                 & $[\,M_{\odot}\,]$    & $[\,M_{\odot}\,]$ & $[\,\text{pc}\,]$ \\
$5$              & $2.4\times10^6$      & $4.8\times10^5$   & $700$             \\
$4$              & $3\times10^5$        & $6\times10^4$     & $350$             \\
$3$              & $3.75 \times 10^{4}$ & $7500$            & $175$             \\
$2$              & $4690$               & $938$             & $87.5$            \\
$1$              & $586$                & $117$             & $43.8$           
\end{tabular}
\end{table}

\begin{table}
\begin{tabular}{cccc}
resolution level & $m_{\text{DM}}$      & $m_{\text{b}}$    & $\epsilon$        \\
                 & $[\,M_{\odot}\,]$    & $[\,M_{\odot}\,]$ & $[\,\text{pc}\,]$ \\
$5$h             & $2.4\times10^6$      & $4.8\times10^5$   & $700$             \\
$4$h             & $3\times10^5$        & $6\times10^4$     & $350$             \\
$3$h             & $3.75 \times 10^{4}$ & $7500$            & $175$             \\
$2$h             & $4690$               & $938$             & $87.5$            \\
$1$h             & $586$                & $117$             & $43.8$           
\end{tabular}
\end{table}

>>>>

\newcommand{\arepo}{\textsc{Arepo}}

@@

% Abstract of the paper
\begin{abstract}
Long-term, secular processes can be important drivers of present-day galactic
properties. The Milky Way is known to host one and perhaps multiple bars whose
gravitational influence has observable consequences on both stellar and
gaseous components. It has long been known that along the major axis of a bar
gas can be driven towards the galactic center, fueling, e.g., the Central
Molecular Zone and nuclear activity. On the other hand, stars are known to
congregate near Lagrange points (i.e., minimums in the galactic potential),
forming known moving groups such as Hercules. We report the results of
isolated simulations incorporating both a state-of-the-art star formation and
feedback model (in which a multi-phase interstellar medium is generated
self-consistently) and a model of the Milky Way which forms a strong bar with
a pattern speed matched to current observations. We are able to show, for the first time, that an enhancement of star formation may occur at the Lagrange points. We derive a collisional analogue of the theory of dynamical resonances and 
\end{abstract}

@@

\section{Introduction}
Introduction.

\section{Methods}
We perform our simulations using the moving-mesh code \arepo{} \citep{}

@@

\begin{table}
\begin{tabular}{cccc}
resolution level & $m_{\text{DM}}$      & $m_{\text{b}}$    & $\epsilon$        \\
                 & $[\,M_{\odot}\,]$    & $[\,M_{\odot}\,]$ & $[\,\text{pc}\,]$ \\
$5$              & $2.4\times10^6$      & $4.8\times10^5$   & $80$             \\
$4$              & $3\times10^5$        & $6\times10^4$     & $40$             \\
$3$              & $3.75 \times 10^{4}$ & $7500$            & $20$             \\
$2$              & $4690$               & $938$             & $10$            \\
$1$              & $586$                & $117$             & $5$           
\end{tabular}
\end{table}

\begin{table}
\begin{tabular}{cccc}
resolution level & $m_{\text{DM}}$      & $m_{\text{b}}$    & $\epsilon$        \\
                 & $[\,M_{\odot}\,]$    & $[\,M_{\odot}\,]$ & $[\,\text{pc}\,]$ \\
$5$h             & $2.4\times10^6$      & $4.8\times10^5$   & $80$             \\
$4$h             & $3\times10^5$        & $6\times10^4$     & $40$             \\
$3$h             & $3.75 \times 10^{4}$ & $7500$            & $20$             \\
$2$h             & $4690$               & $938$             & $10$            \\
$1$h             & $586$                & $117$             & $5$           
\end{tabular}
\end{table}
